### 2013-10-16 inst/examples/sensitivity-allen.Rmd
updates to sensitivity, notes in sensitivity.Rmd

```{r plotting-options, cache=FALSE, message=FALSE, warning=FALSE, include=FALSE}
rm(list=ls())
source("~/.knitr_defaults.R")
opts_knit$set(upload.fun = socialR::flickr.url)
library(knitcitations)
library(nonparametricbayes) 
```

@@

Replicate data-sets from the same model

@@

@@

>>>>

```{r plotting-options, cache=FALSE, message=FALSE, warning=FALSE ,include=FALSE}
rm(list=ls())
source("~/.knitr_defaults.R")
opts_knit$set(upload.fun = socialR::flickr.url)
library(knitcitations)
library(nonparametricbayes) 
```

@@

Replicate data-sets from the same model, varying both model parameters and data simulation seed

@@

<!--

@@

-->

### 2013-10-16 inst/examples/sensitivity.Rmd
updates to sensitivity, notes in sensitivity.Rmd

### Model and parameters

>>>>

```{r}
models <- c("Myers","Allen")

parameters <- list(Myers = list(
  c(1.5 + rnorm(1, 0, .1), 2.5 + rnorm(1, 0, .1), 8 + rnorm(1, 0, .2)),
  c(1.5 + rnorm(1, 0, .1), 2.5 + rnorm(1, 0, .1), 8 + rnorm(1, 0, .2)),
  c(1.5 + rnorm(1, 0, .1), 2.5 + rnorm(1, 0, .1), 8 + rnorm(1, 0, .2)))
                   Allen = list(
  c(2 + rnorm(1, 0, .1), 8 + rnorm(1, 0, .1), 5 + rnorm(1, 0, .2)),
  c(2 + rnorm(1, 0, .1), 8 + rnorm(1, 0, .1), 5 + rnorm(1, 0, .2)),
  c(2 + rnorm(1, 0, .1), 8 + rnorm(1, 0, .1), 5 + rnorm(1, 0, .2)))
                   )
nuisance_pars <- c("sigma_g", )
nuisance_values <- list(sigma_g = c(0.01, 0.05, 0.1, 0.2))
replicates <- c(1111, 2222, 3333, 4444, 5555, 6666, 7777, 8888) # seeds
```

Rather than loop over in brute force way:

```{r eval=FALSE}

lapply(models, function(m){
  if(m == "Myers")
    f <- Myers
  else if(m == "Allen")
    f <- RickerAllee
  lapply(parameters[[m]], function(p)
    lapply(nuisance_pars, function(n)
      lapply(nuisance_values[[n]], function(v)
        lapply(replicates)

We do better to launch seperate scripts and write to a common data format.

We define a function that takes as arguments all things we wish to vary in the senstivity analysis, and returns a data.frame with the values of interest

```{r eval=FALSE}
sensitivity <- function(model, parameters, nuisance, seed){

data.frame(model = model, pars = as.list(parameters), x = x)
}
```

The data frame isn't a minimal representation: we intentionally replicate
